Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}

### 2019-12-03 papers/marlowe2019/paper.tex

%\clearpage
\section{The Marlowe Playground}

>>>>

\subsubsection{Bound on the maximum number of transactions\label{subsubsec:bound_max_transaction_number}}

\emph{ToDo}
Any transactions that result in errors do not modify the \texttt{State} or the \texttt{Contract}, we know that limiting the analysis to lists of transactions that are shorter than the bound does not lose generality.

\section{The Marlowe Playground}
